### 2023-11-24 paper.tex
Took care of some outstanding todos

\section{Describing an Observational Health Research Workflow Using JuliaHealth}

TODO: Discuss the "big idea" of what this workflow could look like

\subsection{Cohort Expressions Usability}

@@

\subsection{Fine-Grain Creation of Cohorts}

Although OHDSICohortExpressions.jl is sufficient to translate existing phenotype definitions generated in ATLAS to executable queries, oftentimes, there is a tricky problem of how to best iterate on phenotype definitions.
Often, one has to take an existing definition and either revise to a more narrow cohort or write manual code to build more niche cohorts after an initial definition is created.
This refactoring of a phenotype definition can lead to conflating ideas within conversation between expert clinical reviewers, analysts, and health researchers.
This broadly can be the notions of what we are exploring (the phenotype definition; often the responsibility of a clinical reviewer), what is possible to compute upon (the computable phenotype definition; often the responsibility of an analyst), and the goals of the overall study.
For situations such as these, the tool OMOPCDMCohortCreator.jl was created.

@@

TODO: Add reference to phenotype paper
TODO: Add small example showing iterative process 
TODO: Reference capr somehow

@@

\subsection{Building on Current Tools and State of the Art}

@@

With the JuliaHealth tools that have now been created, we can now demonstrate an observational health study workflow that would be used in practice.
For this paper, we used two datasets: a synthetic patient dataset called \textit{Eunomia} and the MIMIC III patient dataset which had been converted into the OMOP CDM to illustrate the workflow provided by the Observational Health sub-ecosystem.
Reproducing the workflow using the \textit{Eunomia} dataset is made readily available at the repository here:

>>>>

\section{Describing Common Observational Health Research Tasks within the Julia Ecosystem}

This section guides readers through common steps part of observational health research and to what capacity the Julia ecosystem supports these tasks.
Here are the steps covered

\begin{enumerate}
  \item \textbf{Using Phenotype Definitions} - brief overview of phenotype definitions and how to work with them
  \item \textbf{Rapid Cohort Iteration and Creation} - how to use JuliaHealth tools to iteratively develop patient cohorts to explore
  \item \textbf{Working with Patient Databases} - current approaches to working with different patient databases
  \item \textbf{Ecosystem Interoperability} - how one can bridge between JuliaHealth's ecosystem to other research ecosystems
\end{enumerate}

\subsection{Using Phenotype Definitions}

@@

\subsection{Rapid Cohort Iteration and Creation}

Although OHDSICohortExpressions.jl is sufficient to translate existing phenotype definitions generated in ATLAS to executable queries, oftentimes, there is a tricky problem of how to best iterate on phenotype definitions. \cite{zelkoDevelopingRobustComputable2023}
Often, one has to take an existing definition and either revise to a more narrow cohort or write manual code to build more niche cohorts after an initial definition is created.
This refactoring of a phenotype definition can lead to conflating ideas within conversation between expert clinical reviewers, analysts, and health researchers.
This broadly can be the notions of what we are exploring (the phenotype definition; often the responsibility of a clinical reviewer), what is possible to compute upon (the computable phenotype definition; often the responsibility of an analyst), and the goals of the overall study.
For situations such as these, the tool OMOPCDMCohortCreator.jl was created.

@@

TODO: Add small example showing iterative process 
TODO: Reference capr somehow

@@

\subsection{Ecosystem Interoperability}

@@

With the JuliaHealth tools that have been created, we can now demonstrate an observational health study workflow that would be used in practice.
For this paper, we used two datasets: a synthetic patient dataset called \textit{Eunomia} and the MIMIC III patient dataset which had been converted into the OMOP CDM to illustrate the workflow provided by the Observational Health sub-ecosystem.
Reproducing the workflow using the \textit{Eunomia} dataset is made readily available at the repository here:
